Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data

### 2020-08-03 article.tex
Bibliography changed

@@

Parkinson's disease is a long-term degenerative disorder of the central nervous system that mainly affects the motor system. As the disease worsens, non-motor symptoms become more common. The symptoms usually emerge slowly. Early in the disease, the most obvious symptoms are shaking, rigidity, slowness of movement, and difficulty with walking. Thinking and behavioral problems may also occur. Recently, resting-state fMRI has become an especially popular area of research, and, as a result, the publication of related articles has grown exponentially \cite{Murphy2013}. The goal of resting-state fMRI is to use the common variance of the fMRI blood oxygenation level dependent (BOLD) signals in different regions of the brain as an indicator of synchronous neural activity \cite{GomezLaberge2011}\cite{Oikonomou2010}. The assumption is that the temporal similarity between the BOLD signals in each region demonstrates that they are in constant communication with one another and thus form a functional network \cite{Calhoun2016}.

There are many ways to define network nodes from fMRI; nodes are often defined as spatial regions of interest, for example, as obtained from fMRI activation or from brain atlases \cite{Arribas2010}\cite{Calhoun2012}. Alternatively, parcellation via a data-driven clustering of the FMRI data itself (e.g., hierarchical clustering or independent component analysis) can be run to define clusters or components (spatial maps with associated time-slices), which can be considered network nodes \cite{Smith2012}. Furthermore, we are curious to find out if fMRI scans carry enough information without taking their temporal connectivities into account. In other words, does spatial information carry enough data to diagnose Parkinson's disease patients?

The majority of fMRI disease diagnosis algorithms are based on temporal information and functional connectivities in some regions of interest (ROIs)\cite{Adali2014}. For instance, Shen et. al had proposed a method based on functional connectivities in some ROIs, which enabled the differentiation of schizophrenic patients from healthy control with an accuracy of $81.3\%$ \cite{Shen2014}. Another powerful model is the hybrid method of static and dynamic resting-state fMRI connectivities proposed by Rashid et. al. The mentioned method uses structural and functional connectivities coherently to classify schizophrenia and bipolar patients accurately ($=89\%$) \cite{Rashid2016}. In contrast to that, there are some powerful methods such as Sarraf and Tofighi's deep 2D convolutional neural network algorithm which can diagnose Alzheimer's disease patients using their proposed adopted LeNet-5 network as accurate as $96.86\%$ \cite{Sarraf2016}. Moreover, Sarraf and Tofighi's method does not make assumptions about the disease, makes it a possible solution for Parkinson's disease diagnosis.

Sarraf and Tofighi's 2D CNN method is one of the best candidates for Parkinson's disease classification. However, it has some downsides which make it unable to do so. First of all, it needs a huge amount of training samples to learn as expected. Secondly, we have to omit some participants to prevent overfitting \cite{Sarraf2016}. Also, this method consumes a lot of hardware resources and the training phase takes hours to complete.

Moreover, there are some other methods, such as the method proposed by Riaz et. al. which is a hybrid approach based on functional connectivity and deep learning to classify ADHD patients. This algorithm divides functional connectivities to different clusters and employs an Elastic Net to select the most discriminant features among the connectivities and the phenotypic information. Finally, a support vector machine will be trained as the classifier \cite{Riaz2020}. This method has shown an acceptable performance on some datasets and can be used for other diseases as well. Unlike our proposed method, this one is still focusing on time-based data such as functional connectivity.

Another eye-catching research is "Detecting Alzheimer’s disease based on 4D fMRI" by Li et. al. This method is empowered by coupling 3D-CNN with long short-term memory (LSTM) together. Similar to the latter algorithm, this one also tries to take advantage of both temporal and structural information inside the 4D images of fMRI. In brief, the mentioned method feeds each time-slice to a different CNNs to extract spatial features. Then the feature maps will be put into an LSTM to capture time-varying features. Subsequently, the output of the last layer will enter a fully-connected layer to do the classification \cite{Li2020}. Although this method is well-engineered, it still utilizes both spatial and temporal information. As mentioned earlier, our method will focus only on spatial data to find out about the potential of it in the task of classification.

"Spatio-temporal deep learning method for ADHD fMRI classification" is another deep learning model by Mao et. al. which worth mentioning. This algorithm is an ensemble method based on three different 3D-CNN and LSTM classifiers. The first network uses a single frame approach and a global average pooling in the end. The second network uses multi-frame CNNs coupled with a max-pooling layer and, the last part implements LSTM layers before pooling. In the end, all of these outputs are fed to a 4D-CNN to train on extracted features \cite{Mao2019}. This method uses both temporal and spatial features together without any assumptions on the data or hand-crafted features and performs astonishing.

@@

\subsection{Data acquisition}
\label{section:data}
fMRI scans were obtained from the OpenfMRI project which was acquired on a 3T Siemens Verio with repetition time (TR) = 2.5 s, echo time (TE) = 30ms, flip angle = 80°. Each sample contains 198 slices of $39 \times 64 \times 64$ voxels from the brains of patients. Subjects were instructed to close their eyes and to rest quietly during the scan session \cite{OpenFmri}.

\subsection{Data pre-processing}
\label{section:preprocessing}
The fMRI data were pre-processed using the standard modules of FMRIB Software Library v5.0 \cite{FMRIB}. The pre-processing steps for the anatomical data involved motion correction (MCFLRIT), skull stripping, and spatial smoothing (Gaussian kernel of 5-mm FWHM). Low level noise was removed using a high-pass temporal filtering. The functional images were then aligned to the individual's high-resolution T1-weighted scans, which were subsequently registered to the Montreal Neurological Institute standard space (MNI152) using affine linear registration. and resampled at 2mm cubic voxels. The product of the preprocessing step was used in the experiments.

\subsection{Three-dimensional convolutional neural networks}
\label{section:3dCnn}
3D Convolutional Neural Networks which are inspired by human visual system are similar to classic neural networks. This architecture has been particularly designed based on the explicit assumption that raw data are three-dimensional that enables us to encode certain properties and also to reduce the amount of hyper parameters. The 3D CNN topology utilizes spatial relationships to reduce the number of parameters which must be learned and thus improves upon general feed-forward back propagation training. Figure \ref{fig:CnnSample} demonstrate the 3D CNN architecture and equation \eqref{eq:CnnVal} shows how value of each voxel is calculated from previous layer based on a fixed kernel \texttt{(size = P$\times$Q$\times$R)} and a bias ($b_{ij}$); where $v^{ xyz }_{ ij }$ is the value of an unit at position ($x,y,z$) in the  \texttt{j}th feature map in the \texttt{i}th layers where $f$ is the activation function, $m$ indexes over the set of
feature maps in the $(i-1)$th layer connected to the current feature map $w^{pqr}_{ijm}$ is the value at the position $(p,q,r)$ of the kernel connected to the $m$th feature map, and $P_i$, $Q_i$ and $R_i$ are the height, width and depth of the kernel, respectively \cite{Ji2013}.

@@

Take medical diagnosis as an example. Besides seeing visible symptoms (or medical images from MRI) and hearing descriptions from patients, a doctor has to look for relations among all the symptoms and preferably infer the corresponding etiology. Only after that can the doctor provide medical advice for the patients \cite{GonzalezCastillo2015}. In this example, although the abilities of seeing and hearing allow the doctor to acquire information from the patients, it is the thinking part that defines a doctor. Specifically, the ability of thinking here could involve causal inference, logic deduction, and dealing with uncertainty, which is apparently beyond the capability of conventional deep learning methods \cite{Wang2016}.

A neural network with arbitrary depth and non-linearities, with dropout applied before every weight layer, is mathematically equivalent to an approximation to the probabilistic deep Gaussian process (GP) \cite{Gal2016}.

Let $\hat{y}$ be the output of a NN model with $L$ layers and a loss function {\it E(·, ·)} such as the softmax loss or the Euclidean loss (square loss).We denote by $W_i$ the NN’s weight matrices of dimensions $K_i \times K_{i-1}$, and by $b_i$ the bias vectors of dimensions $K_i$ for each layer $i = 1, ..., L$. We denote by $y_i$ the observed output corresponding to input $x_i$ for $1 \leq i \leq N$ data points, and the input and output sets as $X, Y$. During NN optimization a regularization term is often added. We often use $L2$ regularization weighted by some weight decay $\lambda$, resulting in a minimization objective (often referred to as cost) and it can written as Equation  \eqref{eq:bayesianCnnDroupout} \cite{Gal2016}.

@@

The posterior distribution $p(\omega|X,Y)$ in Equation \eqref{eq:gpPriority} is intractable. It had been shown that if we use a distribution over matrices whose columns are randomly set to zero, we can recover Equation \eqref{eq:bayesianCnnDroupout} \cite{Gal2016}. Note that previously mentioned distribution $q(\omega)$ can be defined as:

@@

\subsection{Proposed method}
\label{section:proposedMethod}
As mentioned before, our experiment aims to find out if fMRI scans carry any hidden information without taking time-based sequences in action. Accordingly, we examined some previous researches in this field and an eye-catching example of this glance is Sarraf and Tofighi's adopted LeNet-5 architecture \cite{Sarraf2016}. Their algorithm concatenates fMRI images based on depth ($z$) and time ($t$) axis and does not make any assumptions about the disease or the data (except their unknown patient selection criteria), making it a potential applicable solution to different disease diagnosis tasks. In brief, each patient's scan is presented as a huge two-dimensional matrix which is then fed to a CNN network. Although this method has shown huge success in the case of Alzheimer's (based on large ADNI dataset), our experiments clarify that it is not suitable for Parkinson's disease diagnosis with a small dataset (such as OpenfMRI ds000245). In addition to that, Sarraf and Tofighi's method consumes a huge amount of memory and demands a powerful processor due to its large dimensions of data.

@@

\section{Experiments and results}
\label{section:results}
As discussed in Section \ref{section:proposedMethod}, our method does not demand high processing power so we can use a CPU for our experiments. All of the tests had been run on an Intel\textsuperscript{\tiny\textregistered} 4710HQ CPU. Averagely, the training phase takes $1h \; 12m \; 4s$ and the test phase finishes in $6m \; 41s$. As described in Section \ref{section:data}, Parkinson's disease dataset consists of 30 samples of 198 time-slices containing \texttt{$39 \times 64 \times 64$} {\tiny $=(159,744)$} voxels. Also it worth mentioning that the application consumes 270 megabytes of RAM thanks to the TFRECORD file format. Implementation of the proposed method in Python using TensorFlow\textsuperscript{\tiny\textregistered} can we found on \href{https://github.com/amin-amini/BayseanFmriDiseaseDiagnosis}{this Github repository} \cite{SourceCode}.

@@

Also we tested two other methods for comparison, First Sarraf and Tofighi's method \cite{Sarraf2016} which had been described in the beginning of Section \ref{section:proposedMethod} which required a powerful GPU for calculations, had a lot of small assumptions about the data but faced overfitting in all 4 different experiments (Accuracies: [$66.67\%$ , $50\%$ , $50\%$ , $16.67\%$]). Second method is a SVM based method proposed by Rashid et al \cite{Rashid2016} for classification of schizophrenia and bipolar patients based on functional network connectivities. This method takes some assumptions about the data and is not easily expandable to other diseases but I tried it as a competitor (Accuracies: [$83.33\%$ , $66.67\%$ , $66.67\%$ , $16.67\%$]). The comparison can be seen in Table \ref{table:comparison}.

@@

As we can see, the overall shape of the diagrams (loss and accuracy) in Figures \ref{fig:tests_1} to \ref{fig:tests_8} are extremely different than normal CNNs, as can bee seen in Figure \ref{fig:SarrafParkinsonTestResult}. This behavior is the result of using dropouts which prevent gradient descent to smoothly decrease loss \cite{Gal2016}. These smooth steps can be seen in small parts of the diagram but not in the whole diagram. As we add dropout layers, gradient descent tries to minimize the loss of the training. As long as the dropout layers stay the same, everything works as expected. However, as the dropout layers vary, the loss changes dramatically and as a result, the loss diagram becomes noisy.

@@

In this study, we showed that spatial information is powerful enough to diagnose Parkinson's disease. Moreover, we can try to implement a hybrid solution based on the proposed method that uses temporal connectivities as well. For instance, we can use functional connectivity based algorithms \cite{Lehmann2017}\cite{Leonardi2013}\cite{Liu2016}\cite{Liu2015}\cite{Ryali2012} or statistical/Bayesian based methods \cite{Ahmad2016}\cite{Oikonomou2013}\cite{Oikonomou2012}\cite{Power2012}\cite{Suk2016}. Ensembling can be done by training mentioned methods combined with Bayesian units or by adding their extracted features to the existing network.

@@

%% Loading bibliography style file
%\bibliographystyle{model1-num-names}
\bibliographystyle{cas-model2-names}

>>>>

%% Loading bibliography style file
%\bibliographystyle{model1-num-names}
\bibliographystyle{model1a-num-names}\biboptions{authoryear}
%\bibliographystyle{cas-model2-names}

@@

Parkinson's disease is a long-term degenerative disorder of the central nervous system that mainly affects the motor system. As the disease worsens, non-motor symptoms become more common. The symptoms usually emerge slowly. Early in the disease, the most obvious symptoms are shaking, rigidity, slowness of movement, and difficulty with walking. Thinking and behavioral problems may also occur. Recently, resting-state fMRI has become an especially popular area of research, and, as a result, the publication of related articles has grown exponentially \citep{Murphy2013}. The goal of resting-state fMRI is to use the common variance of the fMRI blood oxygenation level dependent (BOLD) signals in different regions of the brain as an indicator of synchronous neural activity \citep{GomezLaberge2011}\citep{Oikonomou2010}. The assumption is that the temporal similarity between the BOLD signals in each region demonstrates that they are in constant communication with one another and thus form a functional network \citep{Calhoun2016}.

There are many ways to define network nodes from fMRI; nodes are often defined as spatial regions of interest, for example, as obtained from fMRI activation or from brain atlases \citep{Arribas2010}\citep{Calhoun2012}. Alternatively, parcellation via a data-driven clustering of the FMRI data itself (e.g., hierarchical clustering or independent component analysis) can be run to define clusters or components (spatial maps with associated time-slices), which can be considered network nodes \citep{Smith2012}. Furthermore, we are curious to find out if fMRI scans carry enough information without taking their temporal connectivities into account. In other words, does spatial information carry enough data to diagnose Parkinson's disease patients?

The majority of fMRI disease diagnosis algorithms are based on temporal information and functional connectivities in some regions of interest (ROIs)\citep{Adali2014}. For instance, Shen et. al had proposed a method based on functional connectivities in some ROIs, which enabled the differentiation of schizophrenic patients from healthy control with an accuracy of $81.3\%$ \citep{Shen2014}. Another powerful model is the hybrid method of static and dynamic resting-state fMRI connectivities proposed by Rashid et. al. The mentioned method uses structural and functional connectivities coherently to classify schizophrenia and bipolar patients accurately ($=89\%$) \citep{Rashid2016}. In contrast to that, there are some powerful methods such as Sarraf and Tofighi's deep 2D convolutional neural network algorithm which can diagnose Alzheimer's disease patients using their proposed adopted LeNet-5 network as accurate as $96.86\%$ \citep{Sarraf2016}. Moreover, Sarraf and Tofighi's method does not make assumptions about the disease, makes it a possible solution for Parkinson's disease diagnosis.

Sarraf and Tofighi's 2D CNN method is one of the best candidates for Parkinson's disease classification. However, it has some downsides which make it unable to do so. First of all, it needs a huge amount of training samples to learn as expected. Secondly, we have to omit some participants to prevent overfitting \citep{Sarraf2016}. Also, this method consumes a lot of hardware resources and the training phase takes hours to complete.

Moreover, there are some other methods, such as the method proposed by Riaz et. al. which is a hybrid approach based on functional connectivity and deep learning to classify ADHD patients. This algorithm divides functional connectivities to different clusters and employs an Elastic Net to select the most discriminant features among the connectivities and the phenotypic information. Finally, a support vector machine will be trained as the classifier \citep{Riaz2020}. This method has shown an acceptable performance on some datasets and can be used for other diseases as well. Unlike our proposed method, this one is still focusing on time-based data such as functional connectivity.

Another eye-catching research is "Detecting Alzheimer’s disease based on 4D fMRI" by Li et. al. This method is empowered by coupling 3D-CNN with long short-term memory (LSTM) together. Similar to the latter algorithm, this one also tries to take advantage of both temporal and structural information inside the 4D images of fMRI. In brief, the mentioned method feeds each time-slice to a different CNNs to extract spatial features. Then the feature maps will be put into an LSTM to capture time-varying features. Subsequently, the output of the last layer will enter a fully-connected layer to do the classification \citep{Li2020}. Although this method is well-engineered, it still utilizes both spatial and temporal information. As mentioned earlier, our method will focus only on spatial data to find out about the potential of it in the task of classification.

"Spatio-temporal deep learning method for ADHD fMRI classification" is another deep learning model by Mao et. al. which worth mentioning. This algorithm is an ensemble method based on three different 3D-CNN and LSTM classifiers. The first network uses a single frame approach and a global average pooling in the end. The second network uses multi-frame CNNs coupled with a max-pooling layer and, the last part implements LSTM layers before pooling. In the end, all of these outputs are fed to a 4D-CNN to train on extracted features \citep{Mao2019}. This method uses both temporal and spatial features together without any assumptions on the data or hand-crafted features and performs astonishing.

@@

\subsection{Data acquisition}
\label{section:data}
fMRI scans were obtained from the OpenfMRI project which was acquired on a 3T Siemens Verio with repetition time (TR) = 2.5 s, echo time (TE) = 30ms, flip angle = 80°. Each sample contains 198 slices of $39 \times 64 \times 64$ voxels from the brains of patients. Subjects were instructed to close their eyes and to rest quietly during the scan session \citep{OpenFmri}.

\subsection{Data pre-processing}
\label{section:preprocessing}
The fMRI data were pre-processed using the standard modules of FMRIB Software Library v5.0 \citep{FMRIB}. The pre-processing steps for the anatomical data involved motion correction (MCFLRIT), skull stripping, and spatial smoothing (Gaussian kernel of 5-mm FWHM). Low level noise was removed using a high-pass temporal filtering. The functional images were then aligned to the individual's high-resolution T1-weighted scans, which were subsequently registered to the Montreal Neurological Institute standard space (MNI152) using affine linear registration. and resampled at 2mm cubic voxels. The product of the preprocessing step was used in the experiments.

\subsection{Three-dimensional convolutional neural networks}
\label{section:3dCnn}
3D Convolutional Neural Networks which are inspired by human visual system are similar to classic neural networks. This architecture has been particularly designed based on the explicit assumption that raw data are three-dimensional that enables us to encode certain properties and also to reduce the amount of hyper parameters. The 3D CNN topology utilizes spatial relationships to reduce the number of parameters which must be learned and thus improves upon general feed-forward back propagation training. Figure \ref{fig:CnnSample} demonstrate the 3D CNN architecture and equation \eqref{eq:CnnVal} shows how value of each voxel is calculated from previous layer based on a fixed kernel \texttt{(size = P$\times$Q$\times$R)} and a bias ($b_{ij}$); where $v^{ xyz }_{ ij }$ is the value of an unit at position ($x,y,z$) in the  \texttt{j}th feature map in the \texttt{i}th layers where $f$ is the activation function, $m$ indexes over the set of
feature maps in the $(i-1)$th layer connected to the current feature map $w^{pqr}_{ijm}$ is the value at the position $(p,q,r)$ of the kernel connected to the $m$th feature map, and $P_i$, $Q_i$ and $R_i$ are the height, width and depth of the kernel, respectively \citep{Ji2013}.

@@

Take medical diagnosis as an example. Besides seeing visible symptoms (or medical images from MRI) and hearing descriptions from patients, a doctor has to look for relations among all the symptoms and preferably infer the corresponding etiology. Only after that can the doctor provide medical advice for the patients \citep{GonzalezCastillo2015}. In this example, although the abilities of seeing and hearing allow the doctor to acquire information from the patients, it is the thinking part that defines a doctor. Specifically, the ability of thinking here could involve causal inference, logic deduction, and dealing with uncertainty, which is apparently beyond the capability of conventional deep learning methods \citep{Wang2016}.

A neural network with arbitrary depth and non-linearities, with dropout applied before every weight layer, is mathematically equivalent to an approximation to the probabilistic deep Gaussian process (GP) \citep{Gal2016}.

Let $\hat{y}$ be the output of a NN model with $L$ layers and a loss function {\it E(·, ·)} such as the softmax loss or the Euclidean loss (square loss).We denote by $W_i$ the NN’s weight matrices of dimensions $K_i \times K_{i-1}$, and by $b_i$ the bias vectors of dimensions $K_i$ for each layer $i = 1, ..., L$. We denote by $y_i$ the observed output corresponding to input $x_i$ for $1 \leq i \leq N$ data points, and the input and output sets as $X, Y$. During NN optimization a regularization term is often added. We often use $L2$ regularization weighted by some weight decay $\lambda$, resulting in a minimization objective (often referred to as cost) and it can written as Equation  \eqref{eq:bayesianCnnDroupout} \citep{Gal2016}.

@@

The posterior distribution $p(\omega|X,Y)$ in Equation \eqref{eq:gpPriority} is intractable. It had been shown that if we use a distribution over matrices whose columns are randomly set to zero, we can recover Equation \eqref{eq:bayesianCnnDroupout} \citep{Gal2016}. Note that previously mentioned distribution $q(\omega)$ can be defined as:

@@

\subsection{Proposed method}
\label{section:proposedMethod}
As mentioned before, our experiment aims to find out if fMRI scans carry any hidden information without taking time-based sequences in action. Accordingly, we examined some previous researches in this field and an eye-catching example of this glance is Sarraf and Tofighi's adopted LeNet-5 architecture \citep{Sarraf2016}. Their algorithm concatenates fMRI images based on depth ($z$) and time ($t$) axis and does not make any assumptions about the disease or the data (except their unknown patient selection criteria), making it a potential applicable solution to different disease diagnosis tasks. In brief, each patient's scan is presented as a huge two-dimensional matrix which is then fed to a CNN network. Although this method has shown huge success in the case of Alzheimer's (based on large ADNI dataset), our experiments clarify that it is not suitable for Parkinson's disease diagnosis with a small dataset (such as OpenfMRI ds000245). In addition to that, Sarraf and Tofighi's method consumes a huge amount of memory and demands a powerful processor due to its large dimensions of data.

@@

\section{Experiments and results}
\label{section:results}
As discussed in Section \ref{section:proposedMethod}, our method does not demand high processing power so we can use a CPU for our experiments. All of the tests had been run on an Intel\textsuperscript{\tiny\textregistered} 4710HQ CPU. Averagely, the training phase takes $1h \; 12m \; 4s$ and the test phase finishes in $6m \; 41s$. As described in Section \ref{section:data}, Parkinson's disease dataset consists of 30 samples of 198 time-slices containing \texttt{$39 \times 64 \times 64$} {\tiny $=(159,744)$} voxels. Also it worth mentioning that the application consumes 270 megabytes of RAM thanks to the TFRECORD file format. Implementation of the proposed method in Python using TensorFlow\textsuperscript{\tiny\textregistered} can we found on \href{https://github.com/amin-amini/BayseanFmriDiseaseDiagnosis}{this Github repository} \citep{SourceCode}.

@@

Also we tested two other methods for comparison, First Sarraf and Tofighi's method \citep{Sarraf2016} which had been described in the beginning of Section \ref{section:proposedMethod} which required a powerful GPU for calculations, had a lot of small assumptions about the data but faced overfitting in all 4 different experiments (Accuracies: [$66.67\%$ , $50\%$ , $50\%$ , $16.67\%$]). Second method is a SVM based method proposed by Rashid et al \citep{Rashid2016} for classification of schizophrenia and bipolar patients based on functional network connectivities. This method takes some assumptions about the data and is not easily expandable to other diseases but I tried it as a competitor (Accuracies: [$83.33\%$ , $66.67\%$ , $66.67\%$ , $16.67\%$]). The comparison can be seen in Table \ref{table:comparison}.

@@

As we can see, the overall shape of the diagrams (loss and accuracy) in Figures \ref{fig:tests_1} to \ref{fig:tests_8} are extremely different than normal CNNs, as can bee seen in Figure \ref{fig:SarrafParkinsonTestResult}. This behavior is the result of using dropouts which prevent gradient descent to smoothly decrease loss \citep{Gal2016}. These smooth steps can be seen in small parts of the diagram but not in the whole diagram. As we add dropout layers, gradient descent tries to minimize the loss of the training. As long as the dropout layers stay the same, everything works as expected. However, as the dropout layers vary, the loss changes dramatically and as a result, the loss diagram becomes noisy.

@@

In this study, we showed that spatial information is powerful enough to diagnose Parkinson's disease. Moreover, we can try to implement a hybrid solution based on the proposed method that uses temporal connectivities as well. For instance, we can use functional connectivity based algorithms \citep{Lehmann2017}\citep{Leonardi2013}\citep{Liu2016}\citep{Liu2015}\citep{Ryali2012} or statistical/Bayesian based methods \citep{Ahmad2016}\citep{Oikonomou2013}\citep{Oikonomou2012}\citep{Power2012}\citep{Suk2016}. Ensembling can be done by training mentioned methods combined with Bayesian units or by adding their extracted features to the existing network.

@@
